\section{Courses}

\begin{itemize}
  \item \textbf{Nvidia CUDA: GPU Parallel Programming} --- LNCC.

    Using \textbf{C} as programming language in the early versions of the SDK.

  \item \textbf{Maratona Behind the Code} {[Jul-Ago, 2019 \& Jul-Ago, 2020]} --- IBM.

    Using \textbf{IBM Cloud}, \textbf{Watson} AI, and the
    \textbf{Hyperledger Fabric} blockchain framework, in addition to
    general knowledge of software development, for solving business
    challenges proposed from different companies of Brazil.

  \item \textbf{Java Programming Masterclass for Software Developers} --- Udemy.

    Using OpenJDK \textbf{v1.8} and \textbf{v11}, covering language syntax,
    internal API, boilerplate configuration and source code, project management
    with \textbf{Apache Maven}, plug-ins, archetypes, and external dependencies.

  \item \textbf{Machine Learning A-Z\texttrademark: Hands-On Python \& R In Data
    Science} --- Udemy.

    Using Spyder and R Studio for creating ML models from public datasets,
    based on industry standards, managing versions of libraries, mostly
  \textbf{SciPy}, running on top of \textbf{Jupyter Notebook}.

  \item \textbf{Docker and Kubernetes: The Complete Guide} --- Udemy.

    Using DevOps with applications from different fields of technology,
    implementing \textbf{CI/CD} on projects, automation of pipelines, high
    available microservices, and non-bloated containers.

  \item \textbf{The Complete Angular Course: Beginner to Advanced} --- Udemy.

  Using Angular \textbf{v2.0}+, adding internationalization, communication
    with back-end API, and creating dynamic web applications in general,
    implemented in \textbf{TypeScript}.

\end{itemize}
