\section{Experience}

\subsection{System Analyst \hfill Mar 2022 --- Present}
\subtext{Sinqia · Full-time · Remote \hfill Sao Paulo, Brazil}

\begin{zitemize}
  \item
    I work on providing support for a private pension system for closed
    entities called Site Participante, being responsible for all
    business-specific modules related to other teams. I perform the initial
    technical analysis and provide support or redirect issues to the
    responsible area.
  \item
    Became a point of reference within a team of ten people, being the first to
    document analyses to support the provided support. I investigated problems
    by debugging the source code of the project built using the .NET Framework
    and procedures.
  \item
    Handle demands from multiple clients in parallel and on various topics,
    meeting the SLA response time, delivering solutions for configuration and
    data adjustments, providing patches for error correction, and mentoring
    team members.
  \item
    Created tools to streamline support by writing dynamic queries to be
    executed in different clients' databases using input parameters. I also
    created an HTML document from the AsciiDoc markup language, which serves as
    support for various teams to access the system and the company's internal
    tools.
\end{zitemize}

\textbf{Skills}: SQL Server · C\# · JavaScript · Git · LibreOffice

\vspace{1em}
\subsection{Technical Writer \hfill Jul 2019 --- Apr 2020}
\subtext{Severalnines · Freelance · Remote \hfill Kalmar County, Sweden}

\begin{zitemize}
  \item
    I was invited to write articles about databases, choosing topics from a
    pre-established list, on subjects such as security, scalability,
    containerization, and modeling.
\end{zitemize}

\textbf{Skills}: Linux · PostgreSQL

\vspace{1em}
\subsection{Entrepreneur \hfill Aug 2011 --- Mar 2022}
\subtext{Bolo de Rolo Artesanal · Self-employed \hfill Rio de Janeiro, Brazil}

\begin{zitemize}
  \item
    Started a company as my first job in partnership with my mother, and we
    operated as a home-based food production industry and service provider,
    specializing in a cultural heritage of the state of Pernambuco called Bolo
    de Rolo.
  \item
    Managed the entire company using open-source tools, from the operating
    system to the development of product labels, as well as financial
    management and inventory control of goods and supplies.
  \item
    I was responsible for the relationship with clients, mostly delicatessens,
    conducting prospecting and deliveries in three cities of the state, and was
    able to maintain the same client portfolio for over ten years due to the
    dedication to the quality of the product.
  \item
    Provided support to the production of goods, actively contributing to all
    stages of product conception, from the beginning with the preparation of
    the recipe to the end with packaging and quality control.
\end{zitemize}

\textbf{Skills}: Linux · LibreOffice · Inkscape · GIMP

\vspace{.5em}
